Uranyl solvation by a three-dimensional reference interaction site model

### 2015-04-17 doc/uo2_paper/uo2-II.tex
AM: graphics from CWD again
AM: bib from CWD
AM: achemso is the default here
AM: rm refs to sections

\title{Uranyl solvation by a three-dimensional reference interaction site
model}
\author{Alexei Matveev}
\email{alexei.matveev@gmail.com}
\author{Bo Li}
\author{Notker Rösch}
\email{roesch@mytum.de}
\affiliation{Department Chemie, Technische Universität München, 85747 Garching,
Germany}
\alsoaffiliation{Catalysis Research Center, Technische Universität München, 85747
Garching, Germany}
\alsoaffiliation{Institute of High Performance Computing, Agency for Science, Technology
and Research, 1 Fusionopolis Way, Connexis \#16-16, Singapore 138632,
Singapore}
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}
%% A simple dot to overcome graphicx limitations
\newcommand{\lyxdot}{.}

@@

In this work, we first describe our implementation of the 3D RISM
approach as well as a numerical treatment of the long-range Coulomb
field of a charged solute, Section~\ref{sec:methodology}. Then we
validate the implementation by comparing the results of 1D and 3D
techniques for alkali and halide ions, Section~\ref{sec:simple-ions}.
We further evaluate the performance of the method for the uranyl(VI)
dication in aqueous solution, represented by aqua complexes $[\text{UO}_{2}(\text{H}_{2}\text{O})_{n}]^{2+}$,
($n=4-6$), using a force field description, Section~\ref{sub:MM+RISM},
and a quantum mechanical representation of the interactions within
the first solvation shell, Section~\ref{sub:QM+RISM}. We also compare
the results to those of PCM calculations. Finally, we analyze the
activation barrier for exchanging a water molecule in the first solvation
shell, Section~\ref{sub:water-exchange}, using QM and MM models
of interactions. With the exception of the water exchange process
the test cases used to evaluate the 3D RISM approach are the same
as in our preceding work on 1D RISM \citep{Bo15}.

@@

\centering{}\includegraphics[width=1\linewidth]{uo2-II\lyxdot d/4w-composite}
\end{figure}
\begin{table}[tbph]
\caption{Average uranyl--water distance, $d$(U--O$_{\text{w}}$), of the first
solvation shell and estimate, $\Delta G_{\text{sol}}$, of the uranyl
solvation energy obtained using gas phase MM (GP) and MM+RISM models
with PSE closures of order $p=1-3$ (PSE$p$), see Eq.~\ref{eq:closure-pse}.$^{a}$
\label{tab:mm-rism}}

@@

\centering{}\includegraphics[width=1\linewidth]{uo2-II\lyxdot d/fig2}
\end{figure}

@@

\centering{}\includegraphics[width=1\linewidth]{uo2-II\lyxdot d/fig3}
\end{figure}

@@

\centering{}\includegraphics[width=1\linewidth]{uo2-II\lyxdot d/pmf}
\end{figure}

@@

\centering{}\includegraphics[width=1\linewidth]{uo2-II\lyxdot d/pmf-2d}
\end{figure}

@@

\centering{}\smallskip{}
\includegraphics[width=1\linewidth]{uo2-II\lyxdot d/profiles}
\end{figure}

@@

\bibliographystyle{achemso}
\bibliography{../bibliography}

\begin{tocentry}
\includegraphics[height=3.5cm]{uo2-II.d/4w-composite}
\end{tocentry}
\end{document}

>>>>

\title{Uranyl solvation by a three-dimensional reference interaction site
model}
\author{Alexei Matveev}
\email{alexei.matveev@gmail.com}
\author{Bo Li}
\author{Notker Rösch}
\email{roesch@mytum.de}
\affiliation{Department Chemie, Technische Universität München, 85747 Garching,
Germany}
\alsoaffiliation{Catalysis Research Center, Technische Universität München, 85747
Garching, Germany}
\alsoaffiliation{Institute of High Performance Computing, Agency for Science, Technology
and Research, 1 Fusionopolis Way, Connexis \#16-16, Singapore 138632,
Singapore}
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

@@

In this work, we first describe our implementation of the 3D RISM
approach as well as a numerical treatment of the long-range Coulomb
field of a charged solute. Then we
validate the implementation by comparing the results of 1D and 3D
techniques for alkali and halide ions.
We further evaluate the performance of the method for the uranyl(VI)
dication in aqueous solution, represented by aqua complexes $[\text{UO}_{2}(\text{H}_{2}\text{O})_{n}]^{2+}$,
($n=4-6$), using a force field description,
and a quantum mechanical representation of the interactions within
the first solvation shell. We also compare
the results to those of PCM calculations. Finally, we analyze the
activation barrier for exchanging a water molecule in the first solvation
shell, using QM and MM models
of interactions. With the exception of the water exchange process
the test cases used to evaluate the 3D RISM approach are the same
as in our preceding work on 1D RISM \citep{Bo15}.

@@

\centering{}\includegraphics[width=1\linewidth]{4w-composite}
\end{figure}
\begin{table}[tbph]
\caption{Average uranyl--water distance, $d$(U--O$_{\text{w}}$), of the first
solvation shell and estimate, $\Delta G_{\text{sol}}$, of the uranyl
solvation energy obtained using gas phase MM (GP) and MM+RISM models
with PSE closures of order $p=1-3$ (PSE$p$), see Eq.~\ref{eq:closure-pse}.$^{a}$
\label{tab:mm-rism}}

@@

\centering{}\includegraphics[width=1\linewidth]{fig2}
\end{figure}

@@

\centering{}\includegraphics[width=1\linewidth]{fig3}
\end{figure}

@@

\centering{}\includegraphics[width=1\linewidth]{pmf}
\end{figure}

@@

\centering{}\includegraphics[width=1\linewidth]{pmf-2d}
\end{figure}

@@

\centering{}\smallskip{}
\includegraphics[width=1\linewidth]{profiles}
\end{figure}

@@

\bibliography{bibliography}

\begin{tocentry}
\includegraphics[height=3.5cm]{4w-composite}
\end{tocentry}
\end{document}
